shorts: An R Package for Modeling Short Sprints

### 2021-04-14 paper.Rmd
Fixed few typos

The **shorts** package [@R-shorts], written in the R language [@R-base], represents an open-source tool to help sport scientists translate raw timing data into detailed mechanical outcomes through mathematical modeling [@morinSimpleMethodComputing2019; @samozinoSimpleMethodMeasuring2016]. To best of our knowledge, scientist, researchers, and coaches have been performing short sprints modeling using the built-in solver function of Excel (Microsoft Corporation, Redmond, Washington, United States) [@morinSpreadsheetSprintAcceleration2017; @morinSpreadsheetSprintAcceleration2019; @stenrothForcevelocityProfilingIce2020; @stenrothSpreadsheetSprintAcceleration2020; @samozinoSimpleMethodMeasuring2016; @clarkNFLCombine40Yard2017; @morinSimpleMethodComputing2019], which makes the **shorts** package major improvement in ease-of-use, speed, transparency, reproducibility, and more feature-rich model fitting.

>>>>

The **shorts** package [@R-shorts], written in the R language [@R-base], represents an open-source tool to help sports scientists translate raw timing data into detailed mechanical outcomes through mathematical modeling [@morinSimpleMethodComputing2019; @samozinoSimpleMethodMeasuring2016]. To best of our knowledge, scientist, researchers, and coaches have been performing short sprints modeling using the built-in solver function of Excel (Microsoft Corporation, Redmond, Washington, United States) [@morinSpreadsheetSprintAcceleration2017; @morinSpreadsheetSprintAcceleration2019; @stenrothForcevelocityProfilingIce2020; @stenrothSpreadsheetSprintAcceleration2020; @samozinoSimpleMethodMeasuring2016; @clarkNFLCombine40Yard2017; @morinSimpleMethodComputing2019], which makes the **shorts** package a major improvement in ease-of-use, speed, transparency, reproducibility, and more feature-rich model fitting.

### 2021-04-14 paper.tex
Fixed few typos

The \textbf{shorts} package (\protect\hyperlink{ref-R-shorts}{Jovanovic 2020}), written in the R language (\protect\hyperlink{ref-R-base}{R Core Team 2020}), represents an open-source tool to help sport scientists translate raw timing data into detailed mechanical outcomes through mathematical modeling (\protect\hyperlink{ref-morinSimpleMethodComputing2019}{Jean-Benoit Morin et al. 2019}; \protect\hyperlink{ref-samozinoSimpleMethodMeasuring2016}{Samozino et al. 2016}). To best of our knowledge, scientist, researchers, and coaches have been performing short sprints modeling using the built-in solver function of Excel (Microsoft Corporation, Redmond, Washington, United States) (\protect\hyperlink{ref-morinSpreadsheetSprintAcceleration2017}{J. B. Morin 2017}; \protect\hyperlink{ref-morinSpreadsheetSprintAcceleration2019}{Jean-Benoit Morin and Samozino 2019}; \protect\hyperlink{ref-stenrothForcevelocityProfilingIce2020}{Stenroth, Vartiainen, and Karjalainen 2020}; \protect\hyperlink{ref-stenrothSpreadsheetSprintAcceleration2020}{Stenroth and Vartiainen 2020}; \protect\hyperlink{ref-samozinoSimpleMethodMeasuring2016}{Samozino et al. 2016}; \protect\hyperlink{ref-clarkNFLCombine40Yard2017}{Clark et al. 2017}; \protect\hyperlink{ref-morinSimpleMethodComputing2019}{Jean-Benoit Morin et al. 2019}), which makes the \textbf{shorts} package major improvement in ease-of-use, speed, transparency, reproducibility, and more feature-rich model fitting.

>>>>

The \textbf{shorts} package (\protect\hyperlink{ref-R-shorts}{Jovanovic 2020}), written in the R language (\protect\hyperlink{ref-R-base}{R Core Team 2020}), represents an open-source tool to help sports scientists translate raw timing data into detailed mechanical outcomes through mathematical modeling (\protect\hyperlink{ref-morinSimpleMethodComputing2019}{Jean-Benoit Morin et al. 2019}; \protect\hyperlink{ref-samozinoSimpleMethodMeasuring2016}{Samozino et al. 2016}). To best of our knowledge, scientist, researchers, and coaches have been performing short sprints modeling using the built-in solver function of Excel (Microsoft Corporation, Redmond, Washington, United States) (\protect\hyperlink{ref-morinSpreadsheetSprintAcceleration2017}{J. B. Morin 2017}; \protect\hyperlink{ref-morinSpreadsheetSprintAcceleration2019}{Jean-Benoit Morin and Samozino 2019}; \protect\hyperlink{ref-stenrothForcevelocityProfilingIce2020}{Stenroth, Vartiainen, and Karjalainen 2020}; \protect\hyperlink{ref-stenrothSpreadsheetSprintAcceleration2020}{Stenroth and Vartiainen 2020}; \protect\hyperlink{ref-samozinoSimpleMethodMeasuring2016}{Samozino et al. 2016}; \protect\hyperlink{ref-clarkNFLCombine40Yard2017}{Clark et al. 2017}; \protect\hyperlink{ref-morinSimpleMethodComputing2019}{Jean-Benoit Morin et al. 2019}), which makes the \textbf{shorts} package a major improvement in ease-of-use, speed, transparency, reproducibility, and more feature-rich model fitting.
